---
title: "CFA"
author: "Taylor Brown"
date: '2022-02-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(dplyr)

```

##First
#Install CFA & EFA packages with Lavaan & Lavaan Plot

```{r}
install.packages("lavaan")
install.packages("lavaanPlot")
install.packages("semTools")
install.packages("semPlot")
install.packages("psych")

```
##Second
#run packages

```{r}
library (lavaan)
library(lavaanPlot)
library (semPlot)
library(semTools)
library(psych)

```

##third 
#import the dataset

##Specify the different models
```{r}
onefactormodel <- "useravatar =~ W2_Dis1 + W2_Dis2 + W2_Dis6 + W2_Dis7 + W2_Dis8Rev + W2_Dis9 + W2_Dis10Rev + W2_Dis15Rev"
```

##Fit the model

#Fit the model and save the results
```{r}
fit1 <- cfa(onefactormodel, data = CFA_Data, estimator= "DWLS")

summary(fit1, fit.measures=TRUE, standardized=TRUE)
```


##Saved the table for fit 1
```{r}
tableformat1<-summary(fit1, fit.measures=TRUE, standardized=TRUE) 

modificationindices(fit1, sort. = TRUE)

```

##Get Omega reliability for factors using 'semTools' package

```{r}

reliability(fit1, omit.imps = c("no.conv", "no.se"))


```

##graph the model
```{r}
lavaanPlot(model = fit1, edge_options = list(color = "grey"))

lavaanPlot(model = fit1, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coef = FALSE)
```

##same model with different estimator ML

```{r}
Fit2 <- cfa(onefactormodel, data = CFA_Data, estimator = "MLM")

summary(Fit2, fit.measures=TRUE, standardized=TRUE)

tableformat2<-summary(Fit2, fit.measures=TRUE, standardized=TRUE)

modificationindices(Fit2, sort. = TRUE)

reliability(Fit2, omit.imps = c("no.conv", "no.se"))

lavaanPlot(model = Fit2, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coef = FALSE)
```

##same model with different estimator WLS

```{r}
fit3 <- cfa(onefactormodel, data = CFA_Data, estimator = "WLS")

summary(fit3, fit.measures=TRUE, standardized=TRUE)

tableformat3<-summary(fit3, fit.measures=TRUE, standardized=TRUE)

modificationindices(fit3, sort. = TRUE)

reliability(fit3, omit.imps = c("no.conv", "no.se"))

```

##THE END##
